Capturing underlying musical structure: an audio-based approach to the \textit{Ursatz} using stems and deep learning

### 2023-02-09 music analysis/MSA.tex
Updates from Overleaf

@@

\subsubsection{Homogeneity and novelty}
Homogeneity assumes that segments are homogeneous in musical attributes, with boundaries between dissimilar segments being points of novelty.

@@

>>>>

MSA encompasses various aspects of music analysis, including algorithms, current practices, and trends in technology. This field aims to comprehensively understand music structure by applying musicological theories and principles and music signal processing algorithms. MSA considers the interplay between technical and musical aspects, focusing on improving our understanding of music signals and the music itself.

In the following section, we will examine the state of MSA, including its challenges and potential for future advancements. Topics such as data representation, computational complexity, and evaluation metrics will be discussed to provide a nuanced summary of the field. Additionally, we will consider the impact of new trends and technological advancements on MSA and the directions in which the field is likely to evolve. Through this examination, we aim to provide a thorough understanding of the technical and musical aspects of MSA and its challenges.

@@

\subsubsection{Homogeneity and novelty}
Homogeneity assumes that segments are homogeneous in musical attributes, with boundaries between distinct segments being points of novelty.

@@

\subsection{Aural skills}

Aural music skills are the capacity to comprehend and analyze musical compositions through listening. These skills encompass a wide range of abilities, including identifying musical elements such as rhythm, melody, harmony, timbre, and form, performing music from memory, and transcribing audio recordings into written musical scores.

In the context of music, having strong aural skills is crucial for achieving a complete understanding of the art form. It enables musicians to make knowledgeable decisions about their playing and interpretation, as well as to evaluate the playing of others critically. Additionally, aural skills are an integral part of music education, playing a role in deepening one's appreciation of music and promoting creativity and musical expression.

Aural skills can be honed through various activities, such as listening to music, singing, playing musical instruments, and analyzing music through written or visual means. Formal music education teaches aural skills through ear training, dictation, and sight-reading exercises.

Aural music skills are crucial not only for an individual's personal musical growth but also for gaining a deeper understanding of the underlying musical structure of a piece. Identifying and analyzing musical elements through listening allows one to comprehend the relationships between these elements and how they contribute to the overall musical structure. This ability to perceive and understand musical structure is fundamental to making informed decisions and interpretations.

In addition, solid aural skills enable musicians to communicate their musical ideas to others effectively, as well as to more fully comprehend the musical ideas of others. They provide a common ground for musical discussion and collaboration, allowing musicians to create and perform music at a higher level.

Moreover, aural skills also play an essential role in preserving and continuing musical traditions, as they allow musicians to accurately pass down and preserve the musical heritage of their culture. By recognizing and understanding the underlying musical structures of traditional music, musicians can maintain the authenticity of the music and ensure its continuation for future generations.

In conclusion, aural music skills are crucial for personal musical growth and for gaining a deeper understanding of the musical structure, effective musical communication and collaboration, and the preservation of musical traditions.
